Crunching Large Graphs with Commodity Processors

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex
more space edits

We first characterize the performance of our test machine's memory
system. Then we use these results to evaluate the performance of our runtime within a single node.

@@

There has also been much work on user level threading; the First-Class
User Level Threading project \cite{ult} is one example. Our goal is
slightly different; we want many contexts to tolerate memory latency.

>>>>

% We first characterize the performance of our test machine's memory
% system. Then we use these results to evaluate the performance of our runtime within a single node.

@@

There has also been much work on user level threading; the First-Class
User Level Threading project \cite{ult} is one example. We have a
different goal; we want many lightweight contexts to tolerate memory
latency.
